The development of infants' responses to mispronunciations - A Meta-Analysis

### 2018-11-07 Paper_Analyses.tex
developmental focused manuscript, researcher choices analysis

Next to this core theoretically relevant investigation of the shape of
development of infants' mispronunciation sensitivity, we take the
opportunity of a systematic aggregation of data to address open
questions regarding differences in experiment design and whether changes
in procedure and stimuli tap into significantly different aspects of
infants' ability to detect mispronunciations.

In designing their mispronunciation stimuli, Swingley and Aslin (2000)
chose consonant mispronunciations that were likely to confuse adults
(Miller \& Nicely, 1955). Subsequent research has settled on
systematically modulating phonemic features to achieve mispronunciations
of familiar words. By utilizing mispronunciations consisting of phonemic
changes, these experiments examine infants' sensitivity to factors that
change the identity of a word on a measurable level (i.e.~1-feature,
2-features, 3-features, etc.). The importance of controlling for the
degree of phonological mismatch, as measured by number of features
changed, is further highlighted by studies that find graded sensitivity
to both consonant (White \& Morgan, 2008) and vowel (Mani \& Plunkett,
2011) feature changes.

Although most research examining sensitivity to mispronunciations
follows a similar design, there are some notable differences. For
example, Swingley and Aslin (2000) presented infants with pairs of
familiar images, one serving as the labeled target and one as the
unlabeled distractor. In contrast, White and Morgan (2008; see also Mani
\& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented
infants with pairs of familiar (labeled target) and unfamiliar
(unlabeled distractor) objects. By using an unfamiliar object as a
distractor, the infant is presented with a viable option onto which the
mispronounced label can be applied (Halberda, 2003; Markman, Wasow, \&
Hansen, 2003). Infants ages 24 and 30 months associate a novel label
with an unfamiliar object, although only 30-month-olds retained this
label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast,
18-month-olds did not learn to associate a novel label with an
unfamiliar object, providing evidence that this ability is developing
from 18 to 30 months. We may find that if mispronunciation sensitivity
changes as children develop, that this change is modulated by whether
the distractor used is familiar or unfamiliar. Although mispronunciation
sensitivity in the presence of a familiar compared to unfamiliar
distractor has not been directly compared, the baseline preference for
familiar compared to novel stimuli is also thought to change as infants
develop (Hunter \& Ames, 1988). Furthermore, young children have been
found to look longer at objects for which they know the name, compared
to objects of an unknown name (Schafer \& Plukett, 1998). In other
words, in absentia of a label, infants may be more or less likely to
fixate on an unfamiliar object. To account for inherent preferences to
the target or distractor image, mispronunciation experiments typically
compare the increase in fixations to the target image from a silent
baseline to post-labeling or present the same yoked pairs of target and
distractor images in in both a correct and mispronounced labelling
context. Considering this evidence, we may expect that in older, but not
younger, children, the presence of an unfamiliar distractor may lead to
greater mispronunciation sensitivity than in the presence of a familiar
distractor.

Furthermore, when presenting infants with a familiar distractor image,
some studies control the phonological overlap between the labels for the
target and distractor. For example, when examining sensitivity to a
mispronunciation of the target word \enquote{dog}, the vowel
mispronunciation \enquote{dag} would be paired with a distractor image
that shares onset overlap, such as \enquote{duck}. This ensures that
infants can not use the onset of the word to differentiate between the
target and distractor images (Fernald, Swingley, \& Pinto, 2001).
Instead, infants must pay attention to the mispronounced phoneme in
order to successfully detect the change. The influence of distractor
overlap also depends on the position of the mispronunciation in the
word, which can be at word onset, medial, or final positions. Models of
spoken word processing place more or less importance on the position of
a phoneme in a word. The COHORT model (Marslen-Wilson \& Zwitserlood,
1989) describes lexical access in one direction, with the importance of
each phoneme decreasing as its position comes later in the word. In
contrast, the TRACE model (McClelland \& Elman, 1986) describes lexical
access as constantly updating and reevaluating the incoming speech input
in the search for the correct lexical entry, and therefore can recover
from word onset and to a lesser extent medial mispronunciations.

TRACE has also been used to model infants' sensitivity to
mispronunciation location (Mayor \& Plunkett, 2014), finding that as
lexicon size increases, so does sensitivity to onset mispronunciations,
whereas medial mispronunciations do not experience similar growth. In
early language acquisition, infants typically know more consonant
compared to vowel onset words. When tested on their recognition of
familiar words, therefore, younger infants would show greater
sensitivity to onset mispronunciations, which are frequently consonant
mispronunciations. The prevalence of consonant onset words may
contribute to the finding that consonants carry more weight in lexical
processing (C-bias; see Nazzi, Poltrock, \& Von Holzen, 2016 for a
recent review). In mispronunciation sensitivity, this would translate to
consonant mispronunciations impairing word recognition to a greater
degree than vowel mispronunciations. Yet, the handful of studies
directly comparing sensitivity to consonant and vowel mispronunciations
mostly find symmetry as opposed to an asymmetry between consonants and
vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani \&
Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds
(Hojen et al., unpublished) demonstrate similar sensitivity to consonant
and vowel mispronunciations. One study did find weak evidence for
greater sensitivity to consonant compared to vowel mispronunciations
(Swingley, 2016). The English-learning infants tested by Swingley were
older than previous studies (mean age 28 months). In word learning, the
C-bias has been found to develop later in English learning infants
(Floccia, Nazzi, Delle Luche, Poltrock, \& Goslin, 2014; Nazzi, Floccia,
Moquet, \& Butler, 2009). In the current meta-analysis, we attempt to
synthesize studies examining sensitivity to consonant and vowel
mispronunciations across different ages to determine whether infants
generally exhibit more sensitivity to consonant compared to vowel
mispronunciations in familiar word recognition as predicted by a learned
account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007;
Nazzi et al., 2016). We further examine the impact of language family on
mispronunciation sensitivity to consonants and vowels, as C-bias
emergence has been found to have a different developmental trajectory
for Romance (French, Italian) compared to Germanic (British English,
Danish) languages (Nazzi et al., 2016).

{[}KATIE{]} Christina had noted something to herself for this paragraph:
Subset by language?

Finally, mispronunciation sensitivity in infants has been examined in
many different languages, such as English, Spanish, French, Dutch,
German, Catalan, Danish, and Mandarin Chinese (see Summary\_Table).
Infants learning different languages have different ages of acquisition
for words in their early lexicon, leaving direct comparisons between
languages within the same study difficult and as a result rare. Yet,
studies testing infants from different language backgrounds on similar
sets of stimuli find similar sensitivity to mispronunciations
(Ramon-Casas et al., 2009; Ramon-Casas \& Bosch, 2010). Although we do
not explicitly compare overall mispronunciation sensitivity by language
(although see previous paragraph for rationale to test by language
family), we assess evidence of mispronunciation sensitivity from many
different languages using a meta-analytic approach.

Taken together, the studies we have reviewed begin to paint a picture of
the development of mispronunciation sensitivity. Each study contributes
one separate brushstroke and it is only by examining all of them
together that we can achieve a better understanding. In our analysis, we
examine the factors modulating the development of mispronunciation
sensitivity, which are both of theoretical and practical importance.
Meta-analyses can not only help us summarize the current state of
research, but can also help us evaluate theories to drive future
research and make hands-on recommendations for experiment planning.

@@

\begin{tabular}{l|l|l|l|l|l|l|l}
\hline
Paper & Age & Vocabulary & \# Features & Distractor & Distractor name overlap & MP Position & MP Type\\
\hline
Altvater-Mackensen (2010) & 22, 25 & None & 1 & Familiar, Unfamiliar & onset, novel & onset, onset/medial & consonant\\
\hline
Altvater-Mackensen et al. (2014) & 18, 25 & None & 0, 1 & Familiar & onset & onset & consonant\\
\hline
Bailey \& Plunkett (2002) & 18, 24 & Comprehension & 0, 1, 2 & Familiar & no & onset & consonant\\
\hline
Bergelson \& Swingley (2017) & 7, 9, 12, 6 & None & 0, NA & Familiar & no & onset/medial & vowel\\
\hline
Bernier \& White 2017 & 21 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
\hline
Delle Luche et al. (2015) & 20, 19 & None & 0, 1 & Familiar & onset & onset & consonant\_and\_vowel\\
\hline
Durrant et al. (2014) & 19, 20 & None & 0, 1 & Familiar & onset & onset & consonant\_and\_vowel\\
\hline
Hoehle et al. 2006 & 18 & None & 1 & Familiar & no & onset & consonant\\
\hline
Hojen et al. & 20 & Comprehension/Production & 2\_3 & Familiar & coda, onset & onset/medial, coda/medial & consonant\_and\_vowel, vowel, consonant\\
\hline
Mani \& Plunkett 2007 & 15, 18, 24, 14, 21 & Comprehension/Production & 0, 1\_2, 1 & Familiar & onset & onset & vowel, consonant\_and\_vowel, consonant\\
\hline
Mani \& Plunkett 2010 & 12 & Comprehension & 0, 1 & Familiar & onset & medial, onset & vowel, consonant\\
\hline
Mani \& Plunkett 2011 & 23, 17 & None & 0, 1\_2\_3, 1, 2, 3 & Unfamiliar & novel & medial & vowel\\
\hline
Mani, Coleman, \& Plunkett (2008) & 18 & Comprehension/Production & 0, 1 & Familiar & onset & medial & vowel\\
\hline
Ramon-Casas \& Bosch 2010 & 24, 25 & None & NA & Familiar & no & medial & vowel\\
\hline
Ramon-Casas et al. 2009 & 21, 20 & Production & NA & Familiar & no & medial & vowel\\
\hline
Ren \& Morgan, in press & 19 & None & 0, 1 & Unfamiliar & no & onset, coda & consonant\\
\hline
Skoruppa et al. 2013 & 24 & None & 0, 1 & Unfamiliar & onset/medial & coda & consonant\\
\hline
Swingley (2009) & 17 & Comprehension/Production & 0, 1 & Familiar & no & onset, coda & consonant\\
\hline
Swingley (2016) & 27, 28 & Production & 0, 1 & Unfamiliar & novel & onset/medial & consonant\_and\_vowel, consonant, vowel\\
\hline
Swingley \& Aslin (2000) & 20 & Comprehension & 0, 1 & Familiar & no & onset & consonant\_and\_vowel\\
\hline
Swingley \& Aslin (2002) & 15 & Comprehension/Production & 0, 1, 2 & Familiar & no & onset/medial & consonant\_and\_vowel\\
\hline
Swingley 2003 & 19 & Comprehension/Production & 0, 1 & Familiar & onset & onset, medial & consonant\\
\hline
Tamasi (2016) & 30 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
\hline
Tao \& Qinmei 2013 & 12 & None & NA & Familiar & no & NA & tone\\
\hline
Tao et al. 2012 & 16 & Comprehension & NA & Familiar & no & NA & tone\\
\hline
van der Feest \& Fikkert, 2015 & 24, 20 & None & 0, 1 & Familiar & onset & onset & consonant\\
\hline
van der Feest \& Johnson, 2016 & 24 & None & 0, 1 & Familiar & onset & onset & consonant\\
\hline
Wewalaarachchi et al. 2017 & 24 & None & 0, 1 & Unfamiliar & novel & onset/medial/coda & consonant\_vowel\_tone, vowel, consonant, tone\\
\hline
White \& Aslin (2011) & 18 & None & 1 & Unfamiliar & novel & medial & vowel\\
\hline
White \& Morgan (2008) & 18, 19 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
\hline
Zesiger \& Johr 2011 & 14 & None & 0, 1 & Familiar & no & onset, medial & consonant, vowel\\
\hline
Zesiger et al. (2012) & 12, 19 & Comprehension/Production & 0, 1, 2 & Familiar & no & onset & consonant\\
\hline
\end{tabular}

{[}KATIE{]} THIS TABLE IS DEFINITELY NOT FINISHED! {[}CHRISTINA
suggestions: N features should be a range and exclude 0; we could
abbreviate Comperehension/Production to Comp./Prod.,
etcetc{]}{[}KATIE{]} I'll think about how to implement that! Might end
up having to adjust the table by hand, there is a lot of variation
between studies.

@@

The 32 papers we identified as relevant were then coded with as much
detail as possible (Tsuji, Bergmann, \& Cristia, 2014; Bergmann et al.,
2018). For each experiment (note that a paper typically has multiple
experiments), we entered variables describing the publication,
population, experiment design and stimuli, and results. For the present
analyses, we focus on the following characteristics:\\
1 Condition: Were words mispronounced or not;\\
2 Mean age reported per group of infants, in days;\\
3 Vocabulary size, measured by a standardized questionnaire or list;\\
4 Size of mispronunciation, measured in features changed;\\
5 Distractor familiarity: familiar or unfamiliar;\\
6 Phonological overlap between target and distractor: onset,
onset/medial, rhyme, none, novel word;\\
7 Position of mispronunciation: onset, medial, offset, or mixed;\\
8 Type of mispronunciation: consonant, vowel, or both.

@@

\subsection{Figure 1}\label{figure-1}

@@

\subsection{Figure 2}\label{figure-2}

@@

Alternatively, the lack of developmental change in mispronunciation
sensitivity could be due to differences in the types of tasks given to
infants of different ages. In the following section, we investigate the
role that different moderators play in mispronunciation sensitivity. To
investigate the possibility of systematic differences in the tasks
across ages, we additionally include an exploratory analysis of whether
different moderators and experimental design features were included at
different ages.

\subsection{Moderator Analyses}\label{moderator-analyses}

{[}cHRISTINA{]} I WOULD FOLLOW THE OUTLINE IN THE PREVIOUS PARAGRAPH
HERE OR FLIP THE PARAGRAPH AROUND: 1. ARE DIFFERENT MODERATORS USED AT
DIFFERENT AGES? TEST: sIMPLE CHI-SQUARED OF AGE GROUP VERSUS MODERATOR
ASSIGNMENT (AGE GROUP DETERMINED BY LOOKING AT THE YOUNGEST AGE FOR X?)
2. WHICH MODERATORS INFLUENCE MP SENSITIVITY TEST SIMPLE MA WITH
MODERATOR TESTS

OR \enquote{FOR EACH POSSIBLE MODERATOR WHICH COULD INFLIENCE MP
SENSITIVITY, WE FIRST TEST THIS POSSIBILITY AND THEN EVALUATE WHETHER
THERE IS A SYSTEMATIC DIFFERENCE OF MANIPULATING THESE MODERATORS AS
INFANTS MATURE, I.E. WHETHER OLDER INFANTS ARE TESTED ON A MORE
DIFFICULT TASK} ALSO, AS FINAL FOLLOW-UP IT WOULD BE PERFECT TO JUST
SUBSET ALL STUDIES WITH FAMILIAR DISTRACTORS, SAME NUMBER OF FEATURES,
AND CHECK THAT OUR CONCLUSIONS HOLD UP REGARING MP SENSITIVITY

{[}KATIE: I prefer this second option, first looking at the moderators
in general and then looking at whether there is this systematic
difference with age. The latter is exploratory, so I feel like this
information should not preceed our planned analyses.{]}

\subsubsection{Number of features
changed}\label{number-of-features-changed}

To assess whether the number of features changed modulates
mispronunciation sensitivity, we calculated the meta-analytic effect for
object identification in response to words that were pronounced
correctly and mispronounced using 1-, 2-, and 3-feature changes. We did
not include data for which the number of features changed in a
mispronunciation was not specified or the number of features changed was
not consistent (e.g., one mispronunciation included a 2-feature change
whereas another only a 1-feature change). This analysis was therefore
based on a subset of the overall dataset, with 81 experimental
conditions for correct pronunciations, 108 for 1-feature
mispronunciations, 16 for 2-feature mispronunciations, and 6 for
3-feature mispronunciations. Each feature change (from 0 to 3; 0
representing correct pronunciations) was considered to have an equal
impact on mispronunciation sensitivity, following the argument of graded
sensitivity (White \& Aslin, 2008; Mani \& Plunkett 2011).

To understand the relationship between number of features changed and
mispronunciation sensitivity, we evaluated the effect size Hedges'
\emph{g} with number of features changed as a moderator. The moderator
test was significant, QM(1) = 215.761, \emph{p}\textless{} .001. Hedges'
\emph{g} for number of features changed was -0.123 (SE = 0.014), which
indicated that as the number of features changed increased, the effect
size Hedges' \emph{g} significantly decreased (95\% CI{[}-0.151,
-0.096{]}, \emph{p} \textless{} .001). We plot this relationship in
Figure 3. This confirms previous findings of a graded sensitivity to the
number of features changed for both consonant (White \& Morgan, 2008)
and vowel (Mani \& Plunkett, 2011) mispronunciations as well as the
importance of controlling for the degree of phonological mismatch in
experimental design.

\subsection{Figure 3}\label{figure-3}

\begin{figure}[htbp]
\centering
\includegraphics{Paper_Analyses_files/figure-latex/PlotFeatEffect-1.pdf}
\caption{}
\end{figure}

@@

Although we did not have any specific predictions about the relationship
between infant age and the impact of number of features changed on
mispronunciation sensitivity, we included an exploratory analysis to
examine this relationship. When age was also included as a moderator,
the moderator test was significant, QM(1) = 215.761, \emph{p}\textless{}
.001, but the interaction between age and number of features changed was
not significant, \(\beta\) = 0.006, SE = 0.003, 95\% CI{[}0, 0.011{]},
\emph{p}= 0.069. The small effect size for the interaction between age
and number of features changed suggests that the impact of number of
features changed on mispronunciation sensitivity does not change with
infant age.

Although all papers included in the dataset also included correct
pronunciations, not all papers included all three types of feature
changes (i.e.~1-3). The age range for each type of number of features
changed was 372.89 - 920.20 days (\emph{M} = 637.40) for 1-feature
mispronunciations, 377.28 - 920.20 days (\emph{M} = 612.17) for
2-feature mispronunciations, and 544.48 - 920.20 days (\emph{M} =
661.64) for 3-feature mispronunciations. The reader should note that
experimental conditions in which the number of features changed in a
mispronunciation was not specified or the number of features changed was
not consistent (e.g., one mispronunciation included a 2-feature change
whereas another only a 1-feature change) are not included in these
totals. An analysis focusing on the ages where all three numbers of
features changed were tested (i.e.~544.48 - 920.20 days), however, did
not change the pattern of results.

\subsubsection{Distractor familiarity}\label{distractor-familiarity}

We next assessed whether distractor familiarity has an impact on the
size of mispronunciation sensitivity. First, we calculated the
meta-analytic effect for object identification in response to
mispronounced target words/images that were paired with either a
familiar or an unfamiliar distractor image. The moderator test was not
significant QM(1) = 215.761, \emph{p}\textless{} .001 and the estimate
for distractor familiarity was relatively small, \(\beta\) = -0.082, SE
= 0.126, 95\% CI{[}-0.329, 0.164{]}, \emph{p}= 0.513. This suggests that
upon hearing a mispronunciation, infants' looks to the target image were
similar for when the target image was paired with an image of a familiar
or unfamiliar object. We next assessed whether distractor familiarity
was related to mispronunciation sensitivity. We merged the two datasets
and included condition (correct pronunciation, mispronunciation) as an
additional moderator. The moderator test was significant, QM(1) =
215.761, \emph{p}\textless{} .001, but the estimate for the interaction
between distractor familiarity and condition was small and not
significant \(\beta\) = 0.141, SE = 0.081, 95\% CI{[}-0.017, 0.299{]},
\emph{p}= 0.08. This relationship is plotted in Figure 4. The results
suggest that overall, infants' familiarity with the distractor object
(familiar or unfamiliar) did not impact their mispronunciation
sensitivity.

\subsection{Figure 4}\label{figure-4}

\begin{figure}[htbp]
\centering
\includegraphics{Paper_Analyses_files/figure-latex/PlotDistFamEffect_NoAge-1.pdf}
\caption{}
\end{figure}

>>>>

Taken together, the studies we have reviewed begin to paint a picture of
the development of mispronunciation sensitivity. Each study contributes
one separate brushstroke and it is only by examining all of them
together that we can achieve a better understanding. Meta-analyses can
not only help us summarize the current state of research, but can also
help us evaluate theories to drive future research and make hands-on
recommendations for experiment planning.

@@

\begin{tabular}{l|l|l|l}
\hline
Paper & Publication format & Age & Vocabulary\\
\hline
Altvater-Mackensen (2010) & dissertation & 22, 25 & None\\
\hline
Altvater-Mackensen et al. (2014) & paper & 18, 25 & None\\
\hline
Bailey \& Plunkett (2002) & paper & 18, 24 & Comprehension\\
\hline
Bergelson \& Swingley (2017) & paper & 7, 9, 12, 6 & None\\
\hline
Bernier \& White 2017 & proceedings & 21 & None\\
\hline
Delle Luche et al. (2015) & paper & 20, 19 & None\\
\hline
Durrant et al. (2014) & paper & 19, 20 & None\\
\hline
Hoehle et al. 2006 & paper & 18 & None\\
\hline
Hojen et al. & gray paper & 20 & Comprehension/Production\\
\hline
Mani \& Plunkett 2007 & paper & 15, 18, 24, 14, 21 & Comprehension/Production\\
\hline
Mani \& Plunkett 2010 & paper & 12 & Comprehension\\
\hline
Mani \& Plunkett 2011 & paper & 23, 17 & None\\
\hline
Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comprehension/Production\\
\hline
Ramon-Casas \& Bosch 2010 & paper & 24, 25 & None\\
\hline
Ramon-Casas et al. 2009 & paper & 21, 20 & Production\\
\hline
Ren \& Morgan, in press & gray paper & 19 & None\\
\hline
Skoruppa et al. 2013 & paper & 24 & None\\
\hline
Swingley (2009) & paper & 17 & Comprehension/Production\\
\hline
Swingley (2016) & paper & 27, 28 & Production\\
\hline
Swingley \& Aslin (2000) & paper & 20 & Comprehension\\
\hline
Swingley \& Aslin (2002) & paper & 15 & Comprehension/Production\\
\hline
Swingley 2003 & paper & 19 & Comprehension/Production\\
\hline
Tamasi (2016) & dissertation & 30 & None\\
\hline
Tao \& Qinmei 2013 & paper & 12 & None\\
\hline
Tao et al. 2012 & paper & 16 & Comprehension\\
\hline
van der Feest \& Fikkert, 2015 & paper & 24, 20 & None\\
\hline
van der Feest \& Johnson, 2016 & paper & 24 & None\\
\hline
Wewalaarachchi et al. 2017 & paper & 24 & None\\
\hline
White \& Aslin (2011) & paper & 18 & None\\
\hline
White \& Morgan (2008) & paper & 18, 19 & None\\
\hline
Zesiger \& Johr 2011 & paper & 14 & None\\
\hline
Zesiger et al. (2012) & paper & 12, 19 & Comprehension/Production\\
\hline
\end{tabular}

{[}KATIE{]} THIS TABLE IS DEFINITELY NOT FINISHED! {[}CHRISTINA
suggestions: N features should be a range and exclude 0; we could
abbreviate Comperehension/Production to Comp./Prod.,
etcetc{]}{[}KATIE{]} I've reduced the table to be about age and
vocabulary, in order to have it more focused for the aim of this paper.

@@

The 32 papers we identified as relevant were then coded with as much
detail as possible (Tsuji, Bergmann, \& Cristia, 2014; Bergmann et al.,
2018). For each experiment (note that a paper typically has multiple
experiments), we entered variables describing the publication,
population, experiment design and stimuli, and results. For the present
analyses, we focus on the following characteristics:

1 Condition: Were words mispronounced or not;\\
2 Mean age reported per group of infants, in days;\\
3 Vocabulary size, measured by a standardized questionnaire or list;

@@

\subsection{(Insert Figure 1 about
here)}\label{insert-figure-1-about-here}

@@

\subsection{(Insert Figure 2 about
here)}\label{insert-figure-2-about-here}

@@

Alternatively, it is possible that variation in the analysis approach
lead to systematic differences in the size of mispronunciation
sensitivity. Choices about the approach to data analysis have a higher
possibility to be influenced by the shape of the data itself after
collection, and are therefore susceptible to a higher rate of
false-positives (Simmons, Nelson, \& Simonsohn, 2011). Although we did
not have specific predictions about these variables, such as size of
time window analyzed or dependent variable calculated, we included these
variables in our coding scheme for the meta-analysis dataset. As
reported in the Methods section (and discussed in detail below), some of
these variables varied widely across studies. In the following section,
we include an exploratory analysis to investigate the possibility of
systematic differences in the approach to analysis in general and across
infant age.

{[}KATIE{]} I've changed the above paragraph to lead to exploratory
analyses, not moderators. Since the fmailiar/unfamiliar analysis doesn't
really work out except for if we kind of subset and torture the data, I
think its more interesting to talk about how choices of analysis /
researcher degrees of freedom may influence the data

\subsection{Exploratory Analyses}\label{exploratory-analyses}

We identified several variables to assess the influence of data analysis
choices. These variables fall into two types of categories: time-related
and dependent variable related. In the following analyses, we discuss
the theoretical motivation for these data analysis choices, the
variation present in the current meta-analysis dataset, and the
influence these choices have on mispronunciation sensitivity
development.

\subsubsection{Time-related analyses}\label{time-related-analyses}

When designing mispronunciation sensitivity studies, experimenters
choose the length of time each trial is presented. This includes both
the length of time before the target object is named (pre-naming phase)
as well as after (post-naming phase) and is determined prior to data
collection. Across papers, trial length varied from 2750 to 13000 ms,
with a mode of 5000 ms. There was an inverse relationship between infant
age and trial length, such that younger infants were given trials of a
longer length, although this correlation was not significant (\emph{r} =
-0.11, \emph{p} = 0.086). Presumably, younger infants may be given
longer trials because their word recognition abilities may be slower
than older infants (Fernald et al., 1998).

Unlike the length of trial, the length of the post-naming phase analyzed
can be chosen after the experimental data is collected. Interestingly,
half of the experimental conditions were analyzed using the same length
of post-naming phase as the infant heard in the actual experiment 126,
while the other half were analyzed using a shorter length of post-naming
phase, excluding later portions of the post-naming phase 125. Across
papers, the length of the post-naming phase analyzed varied from 1510 to
6000 ms, with a mode of 2000 ms. Similar to trial length, there was an
inverse relationship between infant age and length of post-naming phase
analyzed, such that younger infants were analyzed using a longer length
of post-naming phase, although here the relationship was significant
(\emph{r} = -0.21, \emph{p} \textless{} .001). Again, the choice to
analyze a shorter post-naming time window is likely related to evidence
that speed of processing is slower in younger infants (Fernald et al.,
1998). Furthermore, the proportion of post-naming phase time window
analyzed in comprison to the total post-naming phase presented to
infants significantly decreased with increasing infant age (\emph{r} =
-0.18, \emph{p} = 0.004). Although trial length did not differ by infant
age, the size of the post-naming phase time window analyzed did differ
by infant age.

When analyzing eye-movements, it is important to consider the amount of
time it takes for an eye movement to be initiated in response to a
stimulus. Previous studies examining simple stimulus response latencies
first determined that infants require at least 233 ms to initiate an
eye-movement in response to a stimulus (Canfield \& Haith, 1991). In
mispronunciation sensitivity studies, however, this has often been
extended to 367 ms (e.g.~Swingley \& Aslin, 2000, 2002, 2007). Across
papers, the majority used a similar offset value (between 360 and 370
ms) for analysis (\emph{n} = 151), but offset values ranged from 0 to
500 ms, and were not reported for 36 experimental conditions. We note
that Swingley (2009) also included offset values of 1133 ms to analyze
responses to coda mispronunciations. There was an inverse relationship
between infant age and size of offset, such that younger infants were
given longer offsets, although this correlation was not significant
(\emph{r} = -0.10, \emph{p} = 0.13). This lack of a relationship is
perhaps driven by the field's consensus that an offset of about 367 ms
is appropriate for analyzing word recognition with PTL measures,
including studies that evaluate mispronunciation sensitivity.

Although there are a priori reasons to choose the post-naming time
window (infant age) or offset time (previous studies), these choices may
occur after data collection and are therefore susceptible to a higher
rate of false-positives. Considering that differences in these choice
were systematically different across infant ages, at least for the
post-naming time window, we next explored whether the size of the
analyzed post-naming phase time window or the offset time influenced
sensitivity to mispronunciations.

\subsubsection{Length of post time}\label{length-of-post-time}

We first assessed whether size of post-naming phase analyzed had an
impact on the size of mispronunciation sensitivity. First, we calculated
the meta-analytic effect for object identification in response to
mispronounced target words/images, including post-naming phase size as a
moderator. The moderator test was not significant QM(1) = 215.761,
\emph{p}\textless{} .001 and the estimate for post-naming phase size was
relatively small, \(\beta\) = 0.121, SE = 0.073, 95\% CI{[}-0.022,
0.264{]}, \emph{p}= 0.097. This suggests that upon hearing a
mispronunciation, infants' looks to the target image were similar
regardless of the size of the post-naming phase analyzed. We next
assessed whether post-naming phase size was related to mispronunciation
sensitivity. We merged the two datasets and included condition (correct
pronunciation, mispronunciation) as an additional moderator. The
moderator test was significant, QM(1) = 215.761, \emph{p}\textless{}
.001. The estimate for the interaction between post-naming phase size
and condition was small but significant \(\beta\) = -0.156, SE = 0.051,
95\% CI{[}-0.256, -0.056{]}, \emph{p}= 0.002. This relationship is
plotted in Figure 3a. The results suggest that although the size of the
post-naming phase analyzed did not impact infants' likelihood to fixate
the target upon hearing the mispronunciation, it did significantly
impact mispronunciation sensitivity. Specifically, the difference
between target fixations for correctly pronounced and mispronounced
items (mispronunciation sensitivity) was significantly greater when the
post-naming phase that was shorter in length.

Considering that we also found a relationship between the length of the
post-naming phase analyzed and infant age, such that younger ages had a
longer post-naming phase time window of analysis, we next examined
whether the size of post-naming phase analyzed modulated the development
of mispronunciation sensitivity. For object recognition in response to a
mispronunciation, including age as a moderator resulted in a moderator
test that was not significant QM(1) = 215.761, \emph{p}\textless{} .001,
and a small estimate for the interaction between age and size of
post-naming phase (\(\beta\) = -0.156, SE = 0.051, 95\% CI{[}-0.256,
-0.056{]}, \emph{p}= 0.002. This suggests that upon hearing a
mispronunciation, infant measured looks to the target image were
similar, regardless of infant age or size of the post-naming phase
analyzed. We next assessed whether the relationship between size of the
post-naming phase analyzed and mispronunciation sensitivity was
modulated by age. We merged the two datasets and included condition
(correct pronunciation, mispronunciation) as well as age as additional
moderators. The moderator test was significant QM(1) = 215.761,
\emph{p}\textless{} .001. The estimate for the three-way-interaction
between condition, size of post-naming phase, and age was small, but
significant (\(\beta\) = = NA, SE = NA, 95\% CI{[}NA, NA{]}, \emph{p}NA.
This relationship is plotted in Figure 3b. Smaller post-naming phase
size lead to greater increases in mispronunciation sensitivity with
development. For example, experimental conditions analyzed with a
post-naming phase of 2000 ms or less, mispronunciation sensitivity
increases with infant age, whereas a post-naming phase of greater than
2000 ms leads to either no impact of age on mispronunciation sensitivity
or a negative relationship between age and mispronunciation sensitivity.

\subsection{(Insert Figure 3 about
here)}\label{insert-figure-3-about-here}

@@

\begin{figure}[htbp]
\centering
\includegraphics{Paper_Analyses_files/figure-latex/Plot_post_name_cond_age-1.pdf}
\caption{}
\end{figure}

\subsubsection{Length of offset time}\label{length-of-offset-time}

We next assessed whether offset time had an impact on the size of
mispronunciation sensitivity. First, we calculated the meta-analytic
effect for object identification in response to mispronounced target
words/images, including offset time as a moderator. The moderator test
was not significant QM(1) = 215.761, \emph{p}\textless{} .001 and the
estimate for offset time was very small, \(\beta\) = 0.001, SE = 0, 95\%
CI{[}0, 0.001{]}, \emph{p}= 0.132. This suggests that upon hearing a
mispronunciation, infants' looks to the target image were similar
regardless of the offset time used to analyze the data. We next assessed
whether offset time was related to mispronunciation sensitivity. We
merged the two datasets and included condition (correct pronunciation,
mispronunciation) as an additional moderator. The moderator test was
significant, QM(1) = 215.761, \emph{p}\textless{} .001, but the estimate
for the interaction between offset time and condition was very small and
not significant \(\beta\) = 0, SE = 0, 95\% CI{[}-0.001, 0{]}, \emph{p}=
0.505.

We next examined whether offset time modulated the development of
mispronunciation sensitivity. For object recognition in response to a
mispronunciation, including age as a moderator resulted in a moderator
test that was not significant QM(1) = 215.761, \emph{p}\textless{} .001,
and a very small estimate for the interaction between age and size of
post-naming phase (\(\beta\) = 0, SE = 0, 95\% CI{[}0, 0{]}, \emph{p}=
0.924. This suggests that upon hearing a mispronunciation, infant
measured looks to the target image were similar, regardless of infant
age or offset time. We next assessed whether the relationship between
offset time and mispronunciation sensitivity was modulated by age. We
merged the two datasets and included condition (correct pronunciation,
mispronunciation) as well as age as additional moderators. The moderator
test was significant QM(1) = 215.761, \emph{p}\textless{} .001, but the
three-way-interaction between condition, offset time, and age was very
small and not significant (\(\beta\) = = 0, SE = 0, 95\% CI{[}0, 0{]},
\emph{p}= 0.605.

Taken together, these results suggest that offset time does not modulate
mispronunciation sensitivity. There is no relationship between offset
time and age, and we find no influence of offset time on the development
of mispronunciation sensitivity.

\subsubsection{Dependent variable-related
analyses}\label{dependent-variable-related-analyses}

Mispronunciation studies evaluate infants' proportion of target looks
(PTL) in response to correct and mispronounced words. Experiments
typically include a phase where no naming event has occured, whether
correctly pronounced or mispronounced, which we refer to as the
baseline. The purpose of the baseline is to ensure that infants do not
have systematic preferences for the target or distractor (greater
interest in a cat compared to cup) which may drive PTL scores in the
post-naming phase. As described in the Data Analysis sub-section of the
Methods, there was considerable variation across papers in way that
baseline was calculated, resulting in different measured outcomes or
dependent variables. Over half of the experimental conditions (\emph{n}
= 129) subtracted the PTL score for a pre-naming phase from the PTL
score for a post-naming phase. This results in one value, which is then
compared with a chance value of 0. When positive, this indicates that
infants increased their looks to the target after hearing the naming
label (correct or mispronounced) relative to the pre-naming baseline
PTL. We will refer to this dependent variable as the Difference Score.
Another dependent variable, which was used in 69 experimental
conditions, directly compared compared the post- and pre-naming PTL
scores with one another. This requires two values, one for the
pre-naming phase and one for the post-naming phase. A greater post
compared to pre-naming phase PTL indicates that increased their target
looks after hearing the naming label. We will refer to this dependent
variable as Pre vs.~Post. Finally, the remaining 53 experimental
conditions compared the post-naming PTL score with a chance value of
50\%. Here, the infants' pre-naming phase preferences are not considered
and instead target fixations are evaluated based on the likelihood to
fixate one of two pictures. We will refer to this dependent variable as
Post.
